NumPy---Array Programming in Python

### 2020-01-10 authors.tex
More work on outline
Add authors
This is the tentative list that Ralf, Stefan, and I agreed on.
We went back to ancient history (`git shortlog -sn v0.9.2..HEAD`), and
tried to weigh merge commits (indicative of review effort) and other
contributions like release management, docs, mentoring, and so on.

It is open to discussion, but we think it is fairly reasonable.

\author[1]{Jane Doe}
\affil[1]{Berkeley Institute for Data Science, University of California, Berkeley, CA 94720, USA}

>>>>

\author[1]{Charles R Harris}
\author[2,3,*]{K. Jarrod Millman}
\author[2,*]{St\'efan J. van der Walt}
\author[4,*]{Ralf Gommers}
\author[8]{Pauli Virtanen}
\author[8]{David Cournapeau}
\author[8]{Eric Wieser}
\author[8]{Julian Taylor}
\author[2]{Sebastian Berg}
\author[8]{Nathaniel J. Smith}
\author[8]{Robert Kern}
\author[8]{Matti Picus}
\author[8]{Stephan Hoyer}
\author[8]{Marten van Kerkwijk}
\author[7]{Matthew Brett}
\author[8]{Allan Haldane}
\author[8]{Jaime Fernandez del Rio}
\author[8]{Mark Wiebe}
\author[8]{Pearu Peterson}
\author[8]{David M. Cooke}
\author[8]{Pierre Gerard-Marchant}
\author[5]{Kevin Sheppard}
\author[6]{Tyler J. Reddy}
\author[2]{Warren Weckesser}
\author[8]{Hameer Abbasi}
\author[8]{Christoph Gohlke}
\author[4]{Travis E. Oliphant}
\affil[1]{Independent Researcher}
\affil[2]{Berkeley Institute for Data Science, University of California, Berkeley, CA, USA}
\affil[3]{Division of Biostatistics, University of California, Berkeley, CA, USA}
\affil[4]{Quansight LLC, Austin, TX, USA}
\affil[5]{Department of Economics, University of Oxford, Oxford, UK}
\affil[6]{Los Alamos National Laboratory, Los Alamos, NM, USA}
\affil[7]{School of Psychology, University of Birmingham, Edgbaston, Birmigham, UK}
\affil[8]{These authors still need to review paper!}
\affil[*]{numpy.articles@gmail.com}
